Unknown

### 2024-04-10 ms/ms.qmd
drafted predictions section

#### Parameter estimation and priors

@@

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) |>
  kableExtra::pack_rows("\\aax{} for each light intensity with leaf using \\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "aa_est")),
                        max(which(df_parameters$par_type == "aa_est")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects light intensity, light treatments, and accession on \\aax",
                        min(which(df_parameters$par_type == "aa")),
                        max(which(df_parameters$par_type == "aa")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of native light habitat on accession-level \\aax",
                        min(which(df_parameters$par_type == "ppfd_aa")),
                        max(which(df_parameters$par_type == "ppfd_aa")),
                        escape = FALSE)

@@

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects light intensity and treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. The expected covariance between accessions $i$ and $j$ ($\text{Cov}(i, j)$ ) is:

@@

The assimilatory, plastic, and constitutive hypotheses make different predictions about the relationship between \aax{} and light intensity, light treatment, and native \ppfd{} among accessions. Since these hypotheses are not mutually exclusive, we describe how we assessed support for one, two, or all three hypotheses simultaneously in \autoref{tbl-predictions}.

We evaluated predictions using a combination of parameter estimation and model selection. In all cases, we estimated parameters and confidence intervals as described in @sec-fitting. If the 95% confidence intervals for a parameter did not overlap zero, we considered the parameter to be significantly different from zero. We used leave-one-out cross-validation (LOOIC) to compare the fit of models (\autoref{tbl-models}) using the *R* package **loo** version `r packageVersion("loo")` [@vehtari_practical_2017] to calculate LOOIC values. We considered models with two standard errors of the mean lower LOOIC value to be a better fit to the data; we considered models with LOOIC values within two standard errors of the mean to be have similar support.

```{r, predictions, eval=FALSE, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-predictions
#| tbl-cap: "caption"

* Assimilatory: 
  + average AA2000 - AA150
  + among accession variation in AA2000 - AA150
* Plastic
  + average AAsun - AAshade
  + among accession variation in AAsun - AAshade
* Constitutive
  + cor(PAR, AA) at accession level

Reinforcing interactions (we only consider these because these are ones which could explain why amphi leaves occur in high light habitats)

* Assimilatory * Plastic (reinforcing interaction)
  + AAsun - AAshade greater at 2000 than 150
  + AA2000 - AA150 greater in sun leaves than shade leaves
  + there may be var among accessions, but not correlated with PAR

* Assimilatory * Constitutive (reinforcing interaction)
  + cor(AA2000, PAR) > 0; cor(AA150, PAR) = 0
  + AA2000 - AA150 varies among accessions, correlated with PAR

* Plastic * Constitutive (reinforcing interaction)
  + cor(AAsun, PAR) > 0; cor(AAshade, PAR) = 0
  + AAsun - AAshade varies among accessions, correlated with PAR

* Assimilatory * Plastic * Constitutive (reinforcing interaction)
  + AAsun - AAshade greater at 2000 than 150
  + AA2000 - AA150 greater in sun leaves than shade leaves
  + AAsun - AAshade varies among accession, correlated with PAR
  + AA2000 - AA150 varies among accession, correlated with PAR
  + cor(AAsun2000, PAR) > cor(AAsun150, PAR) and > cor(AAshade2000, PAR) and > cor(AAshade150, PAR) in nonadditive way

| Hypothesis   | Prediction | Model |
|--------------|------------|------------------|
| Assimilatory |  | base model |
| Plastic      |  | base model |
| Constitutive |  | base model |
| Assimilatory * Plastic |  | + intensity $\times$ treatment |
| Assimilatory * Constitutive |  | + accession $\times$ intensity (random) |
| Plastic * Constitutive |  | + accession $\times$ treatment (random) |
| Assimilatory * Plastic * Constitutive |  | + accession $\times$ intensity $\times$ treatment (random) |

>>>>

#### Parameter estimation and priors {#sec-parameters}

@@

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) |>
  kableExtra::pack_rows("\\aax{} for each light intensity with leaf using \\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "aa_est")),
                        max(which(df_parameters$par_type == "aa_est")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of light intensity, light treatments, and accession on \\aax",
                        min(which(df_parameters$par_type == "aa")),
                        max(which(df_parameters$par_type == "aa")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of native light habitat on accession-level \\aax",
                        min(which(df_parameters$par_type == "ppfd_aa")),
                        max(which(df_parameters$par_type == "ppfd_aa")),
                        escape = FALSE)

@@

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects of light intensity and treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. The expected covariance between accessions $i$ and $j$ ($\text{Cov}(i, j)$ ) is:

@@

The assimilatory, plastic, and constitutive hypotheses make different predictions about the relationship between \aax{} and light intensity, light treatment, and native \ppfd{} among accessions. Since these hypotheses are not mutually exclusive, we describe how we assessed support for one, two, or all three hypotheses simultaneously in \autoref{tbl-predictions}. In general, the assimilatory hypothesis was supported if \aax{} was greater at high light intensity than low light intensity. The plastic hypothesis was supported if \aax{} was greater in sun leaves than shade leaves. The constitutive hypothesis was supported if accession-level \aax{} increased with native \ppfd. In interactive models, we only consider positively reinforcing interactions between high light intensity, sun leaves, and native \ppfd{} because these are the only interactions which could explain why amphistomatous leaves are advantageous in high light habitats.

We evaluated predictions using a combination of parameter estimation and model selection. In all cases, we estimated parameters and confidence intervals as described in @sec-fitting. If the 95% confidence intervals for a parameter did not overlap zero, we considered the parameter to be significantly different from zero. We used the leave-one-out cross-validation information criterion (LOOIC) to compare the fit of models (\autoref{tbl-models}) using the *R* package **loo** version `r packageVersion("loo")` [@vehtari_practical_2017] to calculate LOOIC values. Note that LOOIC was calculated only from pointwise likelihood values of the submodel estimating effects of light intensity, light treatments, and accession on \aax{} (see @sec-parameters). We considered models with two standard errors of the mean lower LOOIC value to be a better fit to the data; we considered models with LOOIC values within two standard errors of the mean to be have similar support.

```{r, predictions, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-predictions
#| tbl-cap: "Predictions of competing hypotheses about the relationship between \\aax{} and light intensity, light treatment, and native \\ppfd{} among accessions. The middle column lists specific directional predictions about parameter values and model fit according to leave-one-out cross-validation information criterion (LOOIC), where $\\text{LOOIC}_i$ is the LOOIC value for model $i$. The rightmost column describes the predictions in words and explains how accession-level \\aax{} is calculated in the relevant model."

tribble(
  ~"\\textbf{Hypothesis}", ~"\\textbf{Prediction(s)}", ~"\\textbf{Description}",
  "Assimilatory", "$\\beta_{\\mathrm{AA},2000} > 0$", "Average \\aax{} at high light intensity is greater than that at low light intensity",
  "Plastic", "$\\beta_{\\mathrm{AA},\\text{sun}} > 0$", "Average \\aax{} in sun leaves is greater than that in shade leaves",
  "Constitutive", "$\\beta_{\\mathrm{PPFD,AA}} > 0$", "Accession-level \\aax{} ($\\mathrm{AA}_\\text{acc}$) increases with native \\ppfd",
  "Constitutive", "", "$\\mathrm{AA}_\\text{acc} = \\beta_{\\mathrm{AA}, 0} + \\vec{\\beta}_{\\mathrm{AA}, \\text{acc}}$",
  "Assimilatory $\\times$ Plastic", "$\\beta_{\\mathrm{AA},2000,\\text{sun}} > 0$", "Average \\aax{} is highest at high light intensity in sun leaves",
  "Assimilatory $\\times$ Plastic", "$\\text{LOOIC}_\\text{1} > \\text{LOOIC}_\\text{2}$", "",
  "Assimilatory $\\times$ Constitutive", "$\\beta_{\\mathrm{AA},2000} > 0$", "Average \\aax{} at high light intensity is greater than that at low light intensity",
  "Assimilatory $\\times$ Constitutive", "$\\beta_{\\mathrm{PPFD,AA}} > 0$", "Accession-level \\aax{} at high light intensity ($\\mathrm{AA}_{\\text{acc},2000}$) increases with native \\ppfd",
  "Assimilatory $\\times$ Constitutive", "$\\text{LOOIC}_\\text{1} > \\text{LOOIC}_\\text{3}$", "$\\mathrm{AA}_{\\text{acc},2000} = \\beta_{\\mathrm{AA}, 0} + \\vec{\\beta}_{\\mathrm{AA}, \\text{acc}} + \\vec{\\beta}_{\\mathrm{AA}, 2000, \\text{acc}}$",
  "Plastic $\\times$ Constitutive", "$\\beta_{\\mathrm{AA},\\text{sun}} > 0$", "Average \\aax{} in sun leaves is greater than that in shade leaves",
  "Plastic $\\times$ Constitutive", "$\\beta_{\\mathrm{PPFD,AA}} > 0$", "Accession-level \\aax{} in sun leaves ($\\mathrm{AA}_{\\text{acc},\\text{sun}}$) increases with native \\ppfd",
  "Plastic $\\times$ Constitutive", "$\\text{LOOIC}_\\text{1} > \\text{LOOIC}_\\text{4}$", "$\\mathrm{AA}_{\\text{acc},\\text{sun}} = \\beta_{\\mathrm{AA}, 0} + \\vec{\\beta}_{\\mathrm{AA}, \\text{acc}} + \\vec{\\beta}_{\\mathrm{AA}, \\text{sun}, \\text{acc}}$",
  "Assimilatory $\\times$ Plastic $\\times$ Constitutive", "$\\beta_{\\mathrm{AA},2000,\\text{sun}} > 0$", "Average \\aax{} is highest at high light intensity in sun leaves",
  "Assimilatory $\\times$ Plastic $\\times$ Constitutive", "$\\beta_{\\mathrm{PPFD,AA}} > 0$", "Accession-level \\aax{} at high light intensity in sun leaves ($\\mathrm{AA}_{\\text{acc},2000,\\text{sun}}$) increases with native \\ppfd",
  "Assimilatory $\\times$ Plastic $\\times$ Constitutive", "$\\text{LOOIC}_\\text{3} > \\text{LOOIC}_\\text{5}$", "$\\mathrm{AA}_{\\text{acc},2000,\\text{sun}} = \\beta_{\\mathrm{AA}, 0} + \\vec{\\beta}_{\\mathrm{AA}, \\text{acc}} + \\vec{\\beta}_{\\mathrm{AA}, 2000, \\text{acc}} + \\vec{\\beta}_{\\mathrm{AA}, \\text{sun}, \\text{acc}}$"

) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::add_indent(positions = seq_len(15), level_of_indent = -1, target_cols = 3) |>
  kableExtra::collapse_rows(1, latex_hline = "major", valign = "top",
                            row_group_label_position = "first") |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "1.5in") |>
  kableExtra::column_spec(3, width = "3in")

# * Assimilatory: 
#   + average AA2000 - AA150
#   + among accession variation in AA2000 - AA150
# * Plastic
#   + average AAsun - AAshade
#   + among accession variation in AAsun - AAshade
# * Constitutive
#   + cor(PAR, AA) at accession level
#   
# Reinforcing interactions 
# 
# * Assimilatory * Plastic (reinforcing interaction)
#   + AAsun - AAshade greater at 2000 than 150
#   + AA2000 - AA150 greater in sun leaves than shade leaves
#   + there may be var among accessions, but not correlated with PAR
#   
# * Assimilatory * Constitutive (reinforcing interaction)
#   + cor(AA2000, PAR) > 0; cor(AA150, PAR) = 0
#   + AA2000 - AA150 varies among accessions, correlated with PAR
#   
# * Plastic * Constitutive (reinforcing interaction)
#   + cor(AAsun, PAR) > 0; cor(AAshade, PAR) = 0
#   + AAsun - AAshade varies among accessions, correlated with PAR
#   
# * Assimilatory * Plastic * Constitutive (reinforcing interaction)
#   + AAsun - AAshade greater at 2000 than 150
#   + AA2000 - AA150 greater in sun leaves than shade leaves
#   + AAsun - AAshade varies among accession, correlated with PAR
#   + AA2000 - AA150 varies among accession, correlated with PAR
#   + cor(AAsun2000, PAR) > cor(AAsun150, PAR) and > cor(AAshade2000, PAR) and > cor(AAshade150, PAR) in nonadditive way
#   
# 
# | Hypothesis   | Prediction | Model |
# |--------------|------------|------------------|
# | Assimilatory |  | base model |
# | Plastic      |  | base model |
# | Constitutive |  | base model |
# | Assimilatory * Plastic |  | + intensity $\times$ treatment |
# | Assimilatory * Constitutive |  | + accession $\times$ intensity (random) |
# | Plastic * Constitutive |  | + accession $\times$ treatment (random) |
# | Assimilatory * Plastic * Constitutive |  | + accession $\times$ intensity $\times$ treatment (random) |

### 2024-04-10 ms/ms.tex
drafted predictions section

\subsubsection{Parameter estimation and
priors}\label{parameter-estimation-and-priors}

@@

\multicolumn{2}{l}{\textbf{effects light intensity, light treatments, and accession on \aax}}\\

@@

\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},\text{2000,high}}$} & \cellcolor{gray!10}{effect of high light intensity at \ppfdequals{2000} on \aax{} in sun treatment}\\

@@

We tested for effects of light intensity, light treatment, accession,
and their interactions on \aax. All models included effects of light
intensity and light treatment, as well as random effects of accession
and replicate within accession. More complex models included
interactions between light intensity and light treatment, as well as
random effects of accession on the effects of light intensity and light
treatment. We used a weakly informative normal prior with mean \(0\) and
standard deviation \(10\) for fixed effects light intensity and
treatment. We used a weakly informative normal prior with mean \(-3\)
and standard deviation \(5\) for the the random effect standard
deviation of replicate within accession. We accounted for the
phylogenetic structure among the random effects of accession using an
Ornstein-Uhlenbeck (OU) process (\emph{14}). The expected covariance
between accessions \(i\) and \(j\) (\(\text{Cov}(i, j)\) ) is:

@@

WORKING HERE TO ADD PREDICTIONS AND TABLE

The assimilatory, plastic, and constitutive hypotheses make different
predictions about the relationship between \aax{} and light intensity,
light treatment, and native \ppfd{} among accessions. Since these
hypotheses are not mutually exclusive, we describe how we assessed
support for one, two, or all three hypotheses simultaneously.

We tested competing predictions through a combination of model selection
and parameter estimation from the posterior of fitted models. In all
cases, we estimated parameters and confidence intervals as described in
Section~\ref{sec-fitting}.

We started with a base model that includes fixed effects of light
intensity and light treatment on \aax, a random effect of accession on
\aax, and a linear regression of PAR on accession-level \aax. We next
compared the fit of the base model to a more complex with an interaction
between light intensity and light treatment using LOOIC with the
\textit{R} package \textbf{loo} version 2.7.0 (\emph{15}). These
comparisons allowed us to test the main predictions of each hypothesis
and for a reinforcing interactions between assimilatory and plastic
hypotheses (tab:predictions). However, these models cannot test
predictions when there is an interaction with the constitutive
hypothesis, because this hypothesis posits accession-levels variation in
responses to light intensity and/or light treatment. Therefore, we
tested for significant variation among accessions in light intensity and
light treatment by comparing LOOIC values of models with and without
random interactions between these factors and accession.

\begin{itemize}
\tightlist
\item
  Assimilatory:

  \begin{itemize}
  \tightlist
  \item
    average AA2000 - AA150
  \item
    among accession variation in AA2000 - AA150
  \end{itemize}
\item
  Plastic

  \begin{itemize}
  \tightlist
  \item
    average AAsun - AAshade
  \item
    among accession variation in AAsun - AAshade
  \end{itemize}
\item
  Constitutive

  \begin{itemize}
  \tightlist
  \item
    cor(PAR, AA) at accession level
  \end{itemize}
\end{itemize}

Reinforcing interactions (we only consider these because these are ones
which could explain why amphi leaves occur in high light habitats)

\begin{itemize}
\tightlist
\item
  Assimilatory * Plastic (reinforcing interaction)

  \begin{itemize}
  \tightlist
  \item
    AAsun - AAshade greater at 2000 than 150
  \item
    AA2000 - AA150 greater in sun leaves than shade leaves
  \item
    there may be var among accessions, but not correlated with PAR
  \end{itemize}
\item
  Assimilatory * Constitutive (reinforcing interaction)

  \begin{itemize}
  \tightlist
  \item
    cor(AA2000, PAR) \textgreater{} 0; cor(AA150, PAR) = 0
  \item
    AA2000 - AA150 varies among accessions, correlated with PAR
  \end{itemize}
\item
  Plastic * Constitutive (reinforcing interaction)

  \begin{itemize}
  \tightlist
  \item
    cor(AAsun, PAR) \textgreater{} 0; cor(AAshade, PAR) = 0
  \item
    AAsun - AAshade varies among accessions, correlated with PAR
  \end{itemize}
\item
  Assimilatory * Plastic * Constitutive (reinforcing interaction)

  \begin{itemize}
  \tightlist
  \item
    AAsun - AAshade greater at 2000 than 150
  \item
    AA2000 - AA150 greater in sun leaves than shade leaves
  \item
    AAsun - AAshade varies among accession, correlated with PAR
  \item
    AA2000 - AA150 varies among accession, correlated with PAR
  \item
    cor(AAsun2000, PAR) \textgreater{} cor(AAsun150, PAR) and
    \textgreater{} cor(AAshade2000, PAR) and \textgreater{}
    cor(AAshade150, PAR) in nonadditive way
  \end{itemize}
\end{itemize}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3182}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2727}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4091}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Hypothesis
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Prediction
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Assimilatory & & base model \\
Plastic & & base model \\
Constitutive & & base model \\
Assimilatory * Plastic & & + intensity \(\times\) treatment \\
Assimilatory * Constitutive & & + accession \(\times\) intensity
(random) \\
Plastic * Constitutive & & + accession \(\times\) treatment (random) \\
Assimilatory * Plastic * Constitutive & & + accession \(\times\)
intensity \(\times\) treatment (random) \\
\end{longtable}

>>>>

\subsubsection{Parameter estimation and priors}\label{sec-parameters}

@@

\multicolumn{2}{l}{\textbf{effects of light intensity, light treatments, and accession on \aax}}\\

@@

\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},2000,\text{sun}}$} & \cellcolor{gray!10}{effect of high light intensity at \ppfdequals{2000} on \aax{} in sun treatment}\\

@@

We tested for effects of light intensity, light treatment, accession,
and their interactions on \aax. All models included effects of light
intensity and light treatment, as well as random effects of accession
and replicate within accession. More complex models included
interactions between light intensity and light treatment, as well as
random effects of accession on the effects of light intensity and light
treatment. We used a weakly informative normal prior with mean \(0\) and
standard deviation \(10\) for fixed effects of light intensity and
treatment. We used a weakly informative normal prior with mean \(-3\)
and standard deviation \(5\) for the the random effect standard
deviation of replicate within accession. We accounted for the
phylogenetic structure among the random effects of accession using an
Ornstein-Uhlenbeck (OU) process (\emph{14}). The expected covariance
between accessions \(i\) and \(j\) (\(\text{Cov}(i, j)\) ) is:

@@

The assimilatory, plastic, and constitutive hypotheses make different
predictions about the relationship between \aax{} and light intensity,
light treatment, and native \ppfd{} among accessions. Since these
hypotheses are not mutually exclusive, we describe how we assessed
support for one, two, or all three hypotheses simultaneously in
\autoref{tbl-predictions}. In general, the assimilatory hypothesis was
supported if \aax{} was greater at high light intensity than low light
intensity. The plastic hypothesis was supported if \aax{} was greater in
sun leaves than shade leaves. The constitutive hypothesis was supported
if accession-level \aax{} increased with native \ppfd. In interactive
models, we only consider positively reinforcing interactions between
high light intensity, sun leaves, and native \ppfd{} because these are
the only interactions which could explain why amphistomatous leaves are
advantageous in high light habitats.

We evaluated predictions using a combination of parameter estimation and
model selection. In all cases, we estimated parameters and confidence
intervals as described in Section~\ref{sec-fitting}. If the 95\%
confidence intervals for a parameter did not overlap zero, we considered
the parameter to be significantly different from zero. We used the
leave-one-out cross-validation information criterion (LOOIC) to compare
the fit of models (\autoref{tbl-models}) using the \emph{R} package
\textbf{loo} version 2.7.0 (\emph{15}) to calculate LOOIC values. Note
that LOOIC was calculated only from pointwise likelihood values of the
submodel estimating effects of light intensity, light treatments, and
accession on \aax{} (see Section~\ref{sec-parameters}). We considered
models with two standard errors of the mean lower LOOIC value to be a
better fit to the data; we considered models with LOOIC values within
two standard errors of the mean to be have similar support.

\begin{longtable}{>{\raggedright\arraybackslash}p{1in}>{\raggedright\arraybackslash}p{1.5in}>{\raggedright\arraybackslash}p{3in}}

\caption{\label{tbl-predictions}Predictions of competing hypotheses
about the relationship between \aax{} and light intensity, light
treatment, and native \ppfd{} among accessions. The middle column lists
specific directional predictions about parameter values and model fit
according to leave-one-out cross-validation information criterion
(LOOIC), where \(\text{LOOIC}_i\) is the LOOIC value for model \(i\).
The rightmost column describes the predictions in words and explains how
accession-level \aax{} is calculated in the relevant model.}

\toprule
\textbf{Hypothesis} & \textbf{Prediction(s)} & \textbf{Description}\\
\midrule
Assimilatory & $\beta_{\mathrm{AA},2000} > 0$ & \hspace{-1em}Average \aax{} at high light intensity is greater than that at low light intensity\\
\cmidrule{1-3}\pagebreak[0]
Plastic & $\beta_{\mathrm{AA},\text{sun}} > 0$ & \hspace{-1em}Average \aax{} in sun leaves is greater than that in shade leaves\\
\cmidrule{1-3}\pagebreak[0]
Constitutive & $\beta_{\mathrm{PPFD,AA}} > 0$ & \hspace{-1em}Accession-level \aax{} ($\mathrm{AA}_\text{acc}$) increases with native \ppfd\\
\nopagebreak
 &  & \hspace{-1em}$\mathrm{AA}_\text{acc} = \beta_{\mathrm{AA}, 0} + \vec{\beta}_{\mathrm{AA}, \text{acc}}$\\
\cmidrule{1-3}\pagebreak[0]
Assimilatory $\times$ Plastic & $\beta_{\mathrm{AA},2000,\text{sun}} > 0$ & \hspace{-1em}Average \aax{} is highest at high light intensity in sun leaves\\
\nopagebreak
 & $\text{LOOIC}_\text{1} > \text{LOOIC}_\text{2}$ & \hspace{-1em}\\
\cmidrule{1-3}\pagebreak[0]
Assimilatory $\times$ Constitutive & $\beta_{\mathrm{AA},2000} > 0$ & \hspace{-1em}Average \aax{} at high light intensity is greater than that at low light intensity\\
\nopagebreak
 & $\beta_{\mathrm{PPFD,AA}} > 0$ & \hspace{-1em}Accession-level \aax{} at high light intensity ($\mathrm{AA}_{\text{acc},2000}$) increases with native \ppfd\\
\nopagebreak
 & $\text{LOOIC}_\text{1} > \text{LOOIC}_\text{3}$ & \hspace{-1em}$\mathrm{AA}_{\text{acc},2000} = \beta_{\mathrm{AA}, 0} + \vec{\beta}_{\mathrm{AA}, \text{acc}} + \vec{\beta}_{\mathrm{AA}, 2000, \text{acc}}$\\
\cmidrule{1-3}\pagebreak[0]
Plastic $\times$ Constitutive & $\beta_{\mathrm{AA},\text{sun}} > 0$ & \hspace{-1em}Average \aax{} in sun leaves is greater than that in shade leaves\\
\nopagebreak
 & $\beta_{\mathrm{PPFD,AA}} > 0$ & \hspace{-1em}Accession-level \aax{} in sun leaves ($\mathrm{AA}_{\text{acc},\text{sun}}$) increases with native \ppfd\\
\nopagebreak
 & $\text{LOOIC}_\text{1} > \text{LOOIC}_\text{4}$ & \hspace{-1em}$\mathrm{AA}_{\text{acc},\text{sun}} = \beta_{\mathrm{AA}, 0} + \vec{\beta}_{\mathrm{AA}, \text{acc}} + \vec{\beta}_{\mathrm{AA}, \text{sun}, \text{acc}}$\\
\cmidrule{1-3}\pagebreak[0]
Assimilatory $\times$ Plastic $\times$ Constitutive & $\beta_{\mathrm{AA},2000,\text{sun}} > 0$ & \hspace{-1em}Average \aax{} is highest at high light intensity in sun leaves\\
\nopagebreak
 & $\beta_{\mathrm{PPFD,AA}} > 0$ & \hspace{-1em}Accession-level \aax{} at high light intensity in sun leaves ($\mathrm{AA}_{\text{acc},2000,\text{sun}}$) increases with native \ppfd\\
\nopagebreak
 & $\text{LOOIC}_\text{3} > \text{LOOIC}_\text{5}$ & \hspace{-1em}$\mathrm{AA}_{\text{acc},2000,\text{sun}} = \beta_{\mathrm{AA}, 0} + \vec{\beta}_{\mathrm{AA}, \text{acc}} + \vec{\beta}_{\mathrm{AA}, 2000, \text{acc}} + \vec{\beta}_{\mathrm{AA}, \text{sun}, \text{acc}}$\\
\bottomrule
